Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-14 docs/ms.tex
up

\subsection{Measurement Error}
In this section we  discuss how the shape measurement error 
affects the variance and bias shear inference.
In principle, if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation ().
However, due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
as an estimator of $\epsilon_{\ell}$.
The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
Figure 5 shows the mean square error of the sample mean estimates in comparison with mean ellipticity estimator.
\begin{figure}
\includegraphics[scale=0.48]{fig/errorN8}
\caption{Figure 5 shows how the mean square error of sample mean estimate varies with the number of patches used, while shape measurement error is considered as described in Section 3.4 .
The horizontal line denotes the mean square of mean ellipticity estiimator which does not depend on number of patches. }
\end{figure}

>>>>

\subsection{Measurement Error}
In this section we  discuss how the shape measurement error 
affects the variance and bias of shear inference.
In principle, if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation (7).
However, due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
as an estimator of $\epsilon_{\ell}$.
The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
Figure 5 shows the mean square error of the sample mean estimates in comparison with mean ellipticity estimator.
\begin{figure}
\includegraphics[scale=0.48]{fig/errorN8}
\caption{Figure 5 shows how the mean square error of sample mean estimate varies with the number of patches used, while shape measurement error is considered as described in Section 3.4 .
The horizontal line denotes the mean square of mean ellipticity estiimator which does not depend on number of patches. }
\end{figure}
